Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-10 minimax.tex
restored table n/10 and changed the time for 100 questions

\section{Empirical Evaluation} 
\label{sec:experiments}
%TODO
%\begin{enumerate}
%	\item Reach regret: $n/10$. For this, we need $m^x n$ questions. Wait for more runs (Correct formula)
%Graphs: order symbols in the legend. Reduce number of marks on the X axis.
%MMR and sd with systematically one decimal exactly
%$150$ questions?
%Pessimistic systematically better than XPess?
%\end{enumerate}
We  performed a number of numerical experiments in order to validate our approach and to test the performance of the different elicitation strategies. %Our experiments are described by topic here below. 
We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, containing the true preferences of the agents (i.e. the linear orders) and the weights associated with the chair's scoring rule. 
The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing. 
For generating the weights we first draw $m - 1$ numbers uniformly at random (representing weight ``differences''), normalize and sort them; 
a sequence of convex decreasing weight is then obtained by a decumulative sum.
The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.

@@

\paragraph{Comparison of strategies}
\begin{figure}
	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
	\label{fig:smallSize}
	\includegraphics[width=.45\textwidth]{comparison.png}
\end{figure}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
	\label{tab:biggerSize}
	\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
		\toprule
		{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0 &20.0 & 0.0 & 20.0 & 0.0&  20.0 & 0.0 \\
		50 & 19.82 & 0.04 &	15.59 &0.56	&17.38& 0.7\\
		100 & 19.12	& 0.26&	11.91&	1.26 &15.23& 0.73\\
		150 & 18.06	& 0.47&	8.92&	1.53 &13.38& 1.11\\
		200 & 16.89	& 0.62&6.24&2.02&11.76& 1.03\\
		250 & 15.63 & 0.84&	4.64&1.72&10.56& 0.89\\
		300 & 14.72	& 0.94&	3.01& 1.35 &10.48& 0.87\\
		350 & 13.41	& 1.15& 1.76& 0.95&10.48& 0.86\\
		400 & 11.98	& 0.68&	0.62&0.56 &10.48& 0.86\\
		\bottomrule
	\end{tabular}
\end{table}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
	\label{tab:geometricWeights}
	\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
		\toprule
		{k} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0	&20.0	&0.0	&20.0	&0.0\\
		100	&12.48	&0.93	&15.6	&0.43\\
		200	&7.43	&1.25	&10.95	&1.12\\
		300	&3.47	&1.32	&6.57	&0.79\\
		\bottomrule
	\end{tabular}
\end{table}
Our first experiment concerns small size situations.
\Cref{fig:smallSize} compares some of our strategies in the case $m = 5, n = 10$ (variations around this size yield similar conclusions), where the results are averaged over $200$ runs.
%(The figure also displays the performance of the Elitist strategy, to which we will come back.)
We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $24$s for a complete elicitation session (for $m = 5$, $n = 10$ and $150$ questions), while Extended pessimistic takes $76$s. Notice that although they exhibit a close performance, Pessimistic performs %significantly %better, in the sense that the numbers are 
consistently better than Extended pessimistic in the different runs of the experiment).
\Cref{tab:biggerSize} shows that these conclusions also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be ran repeatedly on such instance.

@@

%\subsection{Absolute evaluation of Pessimistic strategy}
\paragraph{In-dept evaluation of Pessimistic}
\label{sec:lowRegret}
\begin{table}
	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
	\label{tab:lowRegret}
	\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
		\toprule
		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$}\\
		\midrule
		5 & 10 & 1.0 & 60 & 53\\
		5 & 15 & 1.5 & 80 & 79\\
		5 & 20 & 2.0 & 110 & 105\\
		10 & 20 & 2.0 & 340 & 318\\
		10 & 30 & 3.0 & 527 & 479 \\
		15 & 30 & 3.0 & 951 & 914\\
		\bottomrule		
	\end{tabular}
\end{table}
\begin{table}
	\caption{Number of questions needed by the Pessimistic strategy to elicit the complete preference of one agent.}
	\label{tab:fullProfile}
	\begin{tabular}{S[table-figures-integer=2, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=2]}
		\toprule
		m & k \\
		\midrule
		5 & 6.6\\
		10 & 24.8\\
		15 & 48.4\\
		\bottomrule
	\end{tabular}
\end{table}
While in previous experiments we compared Pessimistic to the other strategies, in this set of experiments, we evaluate the Pessimistic strategy in absolute terms. 
We first wonder how many questions should be asked in order to reach a low regret level. Here, we consider a low level to be a tenth of the number of agents ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
The results for various sizes are displayed in \cref{tab:lowRegret}. 
We see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered. Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, in order to to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$. These numbers have to be contrasted with those displayed in \cref{tab:fullProfile}, that estimate the number of questions required to elicit the full preference of an agent. To obtain the data for this table, we constrained the Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.

>>>>

\section{Empirical Evaluation} 
\label{sec:experiments}
%TODO
%\begin{enumerate}
%	\item Reach regret: $n/10$. Add considerations.
%Graphs: Reduce number of marks on the X axis.
%MMR and sd with systematically one decimal exactly
%Pessimistic systematically better than XPess?
%\end{enumerate}
We  performed a number of numerical experiments in order to validate our approach and to test the performance of the different elicitation strategies. %Our experiments are described by topic here below. 
We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, containing the true preferences of the agents (i.e. the linear orders) and the weights associated with the chair's scoring rule. 
The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing. 
For generating the weights we first draw $m - 1$ numbers uniformly at random (representing weight ``differences''), normalize and sort them; 
a sequence of convex decreasing weight is then obtained by a decumulative sum.
The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.

@@

\paragraph{Comparison of strategies}
\begin{figure}
	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
	\label{fig:smallSize}
	\includegraphics[width=.45\textwidth]{comparison.png}
\end{figure}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
	\label{tab:biggerSize}
	\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
		\toprule
		{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0 &20.0 & 0.0 & 20.0 & 0.0&  20.0 & 0.0 \\
		50 & 19.82 & 0.04 &	15.59 &0.56	&17.38& 0.7\\
		100 & 19.12	& 0.26&	11.91&	1.26 &15.23& 0.73\\
		150 & 18.06	& 0.47&	8.92&	1.53 &13.38& 1.11\\
		200 & 16.89	& 0.62&6.24&2.02&11.76& 1.03\\
		250 & 15.63 & 0.84&	4.64&1.72&10.56& 0.89\\
		300 & 14.72	& 0.94&	3.01& 1.35 &10.48& 0.87\\
		350 & 13.41	& 1.15& 1.76& 0.95&10.48& 0.86\\
		400 & 11.98	& 0.68&	0.62&0.56 &10.48& 0.86\\
		\bottomrule
	\end{tabular}
\end{table}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
	\label{tab:geometricWeights}
	\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
		\toprule
		{k} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0	&20.0	&0.0	&20.0	&0.0\\
		100	&12.48	&0.93	&15.6	&0.43\\
		200	&7.43	&1.25	&10.95	&1.12\\
		300	&3.47	&1.32	&6.57	&0.79\\
		\bottomrule
	\end{tabular}
\end{table}
Our first experiment concerns small size situations.
\Cref{fig:smallSize} compares some of our strategies in the case $m = 5, n = 10$ (variations around this size yield similar conclusions), where the results are averaged over $200$ runs.
%(The figure also displays the performance of the Elitist strategy, to which we will come back.)
We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s. Notice that although they exhibit a close performance, Pessimistic performs %significantly %better, in the sense that the numbers are 
consistently better than Extended pessimistic in the different runs of the experiment).
\Cref{tab:biggerSize} shows that these conclusions also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be ran repeatedly on such instance.

@@

%\subsection{Absolute evaluation of Pessimistic strategy}
\paragraph{In-dept evaluation of Pessimistic}
\label{sec:lowRegret}
\begin{table}
	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
	\label{tab:lowRegret}
	\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
		\toprule
		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
		\midrule
		5 & 10 & 1.0 & 60 \\
		5 & 15 & 1.5 & 80 \\
		5 & 20 & 2.0 & 110 \\
		10 & 20 & 2.0 & 340 \\
		10 & 30 & 3.0 & 527 \\
		15 & 30 & 3.0 & 951 \\
		\bottomrule		
	\end{tabular}
\end{table}
\begin{table}
	\caption{Number of questions needed by the Pessimistic strategy to elicit the complete preference of one agent.}
	\label{tab:fullProfile}
	\begin{tabular}{S[table-figures-integer=2, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=2]}
		\toprule
		m & k \\
		\midrule
		5 & 6.6\\
		10 & 24.8\\
		15 & 48.4\\
		\bottomrule
	\end{tabular}
\end{table}
While in previous experiments we compared Pessimistic to the other strategies, in this set of experiments, we evaluate the Pessimistic strategy in absolute terms. 
We first wonder how many questions should be asked in order to reach a low regret level. Here, we consider a low level to be a tenth of the number of agents ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
The results for various sizes are displayed in \cref{tab:lowRegret}. 
We see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered. Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, in order to to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$. These numbers have to be contrasted with those displayed in \cref{tab:fullProfile}, that estimate the number of questions required to elicit the full preference of an agent. To obtain the data for this table, we constrained the Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.
